Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by organization x.}

### 2018-08-15 paper.tex
PBRS example

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wasysym}
\usepackage[lighttt]{lmodern}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{phaistos}

@@

TODO: minimal example showing normalisation

>>>>

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wasysym}
\usepackage[lighttt]{lmodern}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{phaistos}
\usepackage{subcaption}

@@

\begin{example}
  Consider a simple PBRS, where the initial state $g_0$ has an \texttt{Agent}
  and two \texttt{Locations}, each of which is holding an \texttt{Object} (see
  Fig. \ref{pbrs_initial}), and a single reaction rule with probability $1$ that
  takes an \texttt{Object} from a \texttt{Location} and transfers it to the
  \texttt{Agent} (see Fig. \ref{pbrs_rule}). Then, since regions $1$ and $2$ are
  not treated as isomorphic, the reaction rule can be applied in two ways,
  resulting in two different subsequent states in Fig. \ref{pbrs_next_states},
  $g_1$ and $g_2$. Thus, we have two ground probabilistic reaction rules ($n =
  2$) with $p_1 = p_2 = 1$ and $s = 2$. Let $g' = g_1$. Then $|S| = 1$, and
  \[ g_0 \xrightarrowrhd{0.5}_{\mathcal{R}} g_1, \]
  since
  \[ 0.5 = \frac{1}{2} \sum_{(r, r', 1) \in S} 1. \]
  Similarly,
  \[ g_0 \xrightarrowrhd{0.5}_{\mathcal{R}} g_2. \]
\end{example}

\begin{figure}
  \centering
  \includegraphics{models/pbrs_example/initial.pdf}
  \caption{The initial state.}
  \label{pbrs_initial}
\end{figure}

\begin{figure}
  \centering
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/pbrs_example/take_lhs.pdf}
  \end{minipage}
  $\longrightdoublearrowRHD$
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/pbrs_example/take_rhs.pdf}
  \end{minipage}
  \caption{The reaction rule to take an \texttt{Object} from a
    \texttt{Location}.}
  \label{pbrs_rule}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/pbrs_example/1.pdf}
    \caption{$g_1$}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/pbrs_example/2.pdf}
    \caption{$g_2$}
  \end{subfigure}
  \caption{Two possible next states, depending on which \texttt{Object} is
    taken.}
  \label{pbrs_next_states}
\end{figure}
